### 2016-07-26 notions.tex
comments about privacy

\tsnote{Is this the right kind of indistinguishability anyway?  This current notion says, in effect, that $S_0$ and $S_1$ are indistinguishable \emph{with respect to the allowed queries} (assuming that $\aux$ doesn't stupidly leak information.)  But why not try to formalize the intution that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented, period?  (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)   I don't know, this is tricky... Also, if you give~$M$ to the adversary, how do you handle the fact that, under our current syntax, $M$~may contain secret keys, etc.?}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}

>>>>

\tsnote{Is this the right kind of indistinguishability anyway?  This current notion says, in effect, that $S_0$ and $S_1$ are indistinguishable \emph{with respect to the allowed queries} (assuming that $\aux$ doesn't stupidly leak information.)  But why not try to formalize the intution that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented, period?  (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)   That's tricky to define... Also, if you give~$M$ to the adversary, how do you handle the fact that, under our current syntax, $M$~may contain secret keys, etc.?}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}
